Hydrodynamics and rheology of a vesicle doublet suspension

### 2019-07-20 vesicle_code/docs/adhesion/revisions/reviewer2.tex
yny reviewer2

\item\comment{In II. Governing equations and fig. 1: the right panel of the
figure and comments at the end of the section say that the part of
vesicle membranes that is out of the contact zone, including the parts
that are facing the outer fluid, experience an attractive interaction.
This is an artifact due to the long-range potential chosen by the
authors to model the interaction. In most experimental systems, the
adhesive forces leading to cluster formation are either due to direct
bridging of membranes or depletion phenomena that lead to osmotic
pressure gradients. This is the case for RBC aggregation for instance.
In both mechanisms, there is indeed no attractive force between membrane
parts that are out of the contact zone. It is perfectly fine to model
the interaction by an adhesion potential such as represented in fig 1
left, but its use introduces this artifact that should be acknowledged
by the authors. It is also due to the fact that the value of parameter
$\delta$ (the equilibrium distance) is not small compared to vesicle
dimensions. This is a numerical necessity to avoid the need to have
extremely refined meshes but again in experiments, the equilibrium
distance is usually much smaller that vesicle sizes and is more
comparable to molecular sizes (size of bridging molecules or of
depletion-inducing macromolecules). This deserves to be acknowledged
also, even though it may not impact too much the results.}
\begin{itemize}
  \item The referee is correct that vesicles outside of the contact zone
    do not feel a long range attractive interaction.  Our model follows
    the works on red blood cells by Flormann {\em et al.}~Scientific
    Reports (2017) and Hoore {\em et al.}~Soft Matter (2018).  In both
    these papers, the Lennard-Jones potential is used to model the
    adhesive interaction between red blood cells.  
    Results from these modeling works are found to be in good agreement 
    with experiments and other models for adhesion (Ziherl and Svetina, PNAS (2017)).

@@

\item\comment{ Figs 9(right) and 12(right): the stability diagrams are presented
in different parameter spaces for the extensional and shear flow
cases. It would have been interesting to see e.g. the diagram in the
interaction energy vs. flow strength $\chi$ for both cases, for
comparison.}
\begin{itemize}
  \item In the revision for the extensional example we first focus on how an initial vertical displacement 
  may affect the vesicle dynamics in a planar extensional flow (beginning of the new Section III). 
  There we find that a vesicle doublet is not likely to form unless the two vesicles are aligned
  on the converging axis of the straining flow. In the fluid trap simulations we find that
    the reduced area has a large effect
    on determining if the doublet is broken or not, and on the
    inclination angle if the doublet is not broken.  Therefore, we have
    elected to investigate the effect of the reduced area for this
    example.

>>>>

\item\comment{In II. Governing equations and fig. 1: the right panel of the
figure and comments at the end of the section say that the part of
vesicle membranes that is out of the contact zone, including the parts
that are facing the outer fluid, experience an attractive interaction.
This is an artifact due to the long-range potential chosen by the
authors to model the interaction. In most experimental systems, the
adhesive forces leading to cluster formation are either due to direct
bridging of membranes or depletion phenomena that lead to osmotic
pressure gradients. This is the case for RBC aggregation for instance.
In both mechanisms, there is indeed no attractive force between membrane
parts that are out of the contact zone. It is perfectly fine to model
the interaction by an adhesion potential such as represented in fig 1
left, but its use introduces this artifact that should be acknowledged
by the authors. It is also due to the fact that the value of parameter
$\delta$ (the equilibrium distance) is not small compared to vesicle
dimensions. This is a numerical necessity to avoid the need to have
extremely refined meshes but again in experiments, the equilibrium
distance is usually much smaller that vesicle sizes and is more
comparable to molecular sizes (size of bridging molecules or of
depletion-inducing macromolecules). This deserves to be acknowledged
also, even though it may not impact too much the results.}
\begin{itemize}
  \item The referee is correct that the long-range attraction in the L.-J. is an artifact.
   In this work we focus on the adhesion effects on the hydrodynamics 
   of two vesicles drawn together by an external flow.
   Thus the L.-J. type potential is to keep the equilibrium distance, 
   following the works on red blood cells by Flormann {\em et al.}~Scientific
    Reports (2017) and Hoore {\em et al.}~Soft Matter (2018).  In both
    these papers, the Lennard-Jones potential is used to model the
    adhesive interaction between red blood cells.  
    Results from these modeling works are found to be in good agreement 
    with experiments and other models for adhesion (Ziherl and Svetina, PNAS (2017)).

@@

\item\comment{ Figs 9(right) and 12(right): the stability diagrams are presented
in different parameter spaces for the extensional and shear flow
cases. It would have been interesting to see e.g. the diagram in the
interaction energy vs. flow strength $\chi$ for both cases, for
comparison.}
\begin{itemize}
  \item In the revision for the extensional example we first focus on how an initial vertical displacement 
  may affect the vesicle dynamics in a planar extensional flow (beginning of the new Section III). 
  There we find that a vesicle doublet is not likely to form unless the two vesicles are aligned
  on the converging axis of the extensional flow. In the fluid trap simulations we find that
    the reduced area has a large effect
    on determining if the doublet is broken or not, and on the
    inclination angle if the doublet is not broken.  Therefore, we have
    elected to investigate the effect of the reduced area for this
    example.
